Datasets

### 2018-08-30 scripts/01-datasets/01-real/README.Rmd
update readmes with github_markdown_nested format

---
output: github_document
---

@@

The generation of the real datasets is divided in two parts:

>>>>

---
output: dynbenchmark::github_markdown_nested
---

@@

The generation of the real datasets is divided in two parts. We first download all the (annotated) expression files from sites such as GEO. Next, we filter and normalise all datasets, and wrap them into the common trajectory format of [dynwrap](https://www.github.com/dynverse/dynwrap).
